Stool Microbiome Analysis

### 2021-12-08 Rmarkdown/analysis/Fecal_Microbiome_TMAO_Analysis_211105.Rmd
Load PCoA so don't have to rerun everytime. Tweaked graphs. Saved tax table for manuscript.

@@

```{r Original Alpha Diversity Plots}
# Shannon
y_variable <- "Shannon"
x_variable <- "Natural Log of TMAO (uM)"
mdn_cut <- log(median(df2$tmao.x))
# Plot
shannon_plot <- ggplot(df2, aes(x=tmao_log, y=shannon)) +
  geom_point(aes(shape=bmi_cat, color = age_cat)) +
  geom_vline(xintercept = mdn_cut, linetype = "dashed") +
  geom_smooth(method = "lm", se = FALSE, fullrange = F) +
  theme_minimal() + 
  ylab(y_variable) +
  xlab(x_variable) +
  labs(color = "Age bin", shape = "BMI bin") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text = element_text(size = 12), # x and y axis text size
        axis.title = element_text(size = 12), # x and y label text size
        legend.text = element_text(size = 12), # legend text size
        legend.title = element_text(size = 12), # label legend text size
        axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))
shannon_plot

@@

@@

# Unweighted
betaplot_UWU <- plot_ordination(PSOtmao1G, PCoA_UnWU, 
                    color="tmao_mdn",
                    shape = NULL,
                    axes = 1:2) +
  scale_color_brewer(palette = "Dark2", labels = c("Below", "Above")) +
  stat_ellipse(linetype = 1) +
  labs(color = "TMAO Median Threshold") +
  theme_minimal() + 
  theme(axis.text = element_text(size = 12), # x and y axis text size
        axis.title = element_text(size = 12), # x and y label text size
        legend.text = element_text(size = 12), # legend text size
        legend.title = element_text(size = 12), # label legend text size
        axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))

>>>>

Save taxonomy table for manuscript.

```{r Save the taxonomy table for manuscript}
tax_manuscript <- tax_table(PSOtmao)
write.csv(tax_manuscript, "../../Outputs/tables/Microbiome/PSOtmao_taxonomyTable.csv")
```

@@

```{r Original Alpha Diversity Plots}
# Shannon
y_variable <- "Shannon"
x_variable <- "Natural Log of TMAO (uM)"
mdn_cut <- log(median(df2$tmao.x))
# Plot
shannon_plot <- ggplot(df2, aes(x=tmao_log, y=shannon)) +
  geom_point(aes(shape=bmi_cat, color = age_cat)) +
  geom_vline(xintercept = mdn_cut, linetype = "dashed") +
  geom_smooth(method = "lm", se = FALSE, fullrange = F) +
  theme_minimal() + 
  ylab(y_variable) +
  xlab(x_variable) +
  scale_shape_discrete(name="BMI Bin (kg/m^2)", labels=c("18.5-24", "25-29", "30>")) +
  scale_color_brewer(palette = "Dark2",name="Age Bin (yr)", labels=c("18-33", "34-49", "50-65")) +
  theme(axis.text = element_text(size = 12), # x and y axis text size
        axis.title = element_text(size = 12), # x and y label text size
        legend.text = element_text(size = 12), # legend text size
        legend.title = element_text(size = 12), # label legend text size
        axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))
shannon_plot

@@

Load

```{r Load bdiversity calculations}
load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_PCoA_WU.RData")
load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_PCoA_UnWU.RData")
load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_PCoA_BC.RData")

load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_dismax_WU.RData")
load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_dismax_UWU.RData")
load(file = "../../data/processed/microbiome/diversity/PSOtmao1G_dismax_BC.RData")

@@

# Unweighted
betaplot_UWU <- plot_ordination(PSOtmao1G, PCoA_UnWU, 
                    color="tmao_mdn",
                    shape = NULL,
                    axes = 1:2) +
  #scale_color_brewer(palette = "Dark2", labels = c("Below", "Above")) +
  stat_ellipse(linetype = 1) +
  labs(color = "TMAO Median Threshold") +
  theme_minimal() + 
  theme(axis.text = element_text(size = 12), # x and y axis text size
        axis.title = element_text(size = 12), # x and y label text size
        legend.text = element_text(size = 12), # legend text size
        legend.title = element_text(size = 12), # label legend text size
        axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))
